Intrinsic Verification of Parsers and Formal Grammar Theory in Dependent Lambek Calculus (Extended Version)

### 2025-04-21 paper/paper.tex
"correctness"

\section{Introduction}
\label{sec:intro}
Parsing structured data from untrusted input is a ubiquitous task in
computing. Any formally verified software system that interacts with the outside
world must contain some parsing component, and unverified parsers can undermine the overall correctnes theorem for the system.
For example, in an extensive experiment finding bugs in C compilers
\cite{yangFindingUnderstandingBugs}, an early version of CompCert, the formally
verified C compiler, was found to have bugs only in the then
unverified parsing component \cite{leroy_formal_2009}.
The correctness of the compiler only showed that the abstract syntax tree would be compiled correctly, but this is
not very useful if it did not correctly correspond to the actual
source program. Eventually, CompCert
was updated to use a verified parser that implements
an $\LR{1}$ grammar
\cite{jourdanValidatingLRParsers2012}.

>>>>

\section{Introduction}
\label{sec:intro}
Parsing structured data from untrusted input is a ubiquitous task in
computing. Any formally verified software system that interacts with the outside
world must contain some parsing component, and unverified parsers can undermine the overall correctness theorem for the system.
For example, in an extensive experiment finding bugs in C compilers
\cite{yangFindingUnderstandingBugs}, an early version of CompCert, the formally
verified C compiler, was found to have bugs only in the then
unverified parsing component \cite{leroy_formal_2009}.
The correctness of the compiler only showed that the abstract syntax tree would be compiled correctly, but this is
not very useful if it did not correctly correspond to the actual
source program. Eventually, CompCert
was updated to use a verified parser that implements
an $\LR{1}$ grammar
\cite{jourdanValidatingLRParsers2012}.
